A Survey of Quantitative Descriptions of Molecular Structure

### 2012-07-24 paper.tex
Added more to rebuttal

Methods that aim to predict chemical and biological properties
generally require a numerical description of chemical structures. Such
numerical forms range from a set of 3D coordinates which coupled with
appropriate atom types, is sufficient for methods such as quantum
mechanical (QM) approaches and docking to more abstract numerical
descriptions derived from 2D or 3D representations which can be useful
in statistical approaches. It is now possible to evaluate thousands of
numerical descriptors of chemical structure. As will be discussed
later, many of these descriptors are closely related or capture the
same information, allowing one to be substituted for another. The
choice of descriptors is a well-known problem and given a large
collection of them, approaches to identify a suitable subset have been
discussed extensively in the
literature~\cite{Miller:2002aa,Kohavi:1997gf}.

>>>>

Methods that aim to predict chemical and biological properties
generally require a numerical description of chemical structures. Such
numerical forms range from a set of 3D coordinates which coupled with
appropriate atom types, is sufficient for methods such as quantum
mechanical (QM) approaches and docking to more abstract numerical
descriptions derived from 2D or 3D representations which can be useful
in statistical approaches. It is now possible to evaluate thousands of
numerical descriptors of chemical structure. As will be discussed
later, many of these descriptors are closely related or capture the
same information, allowing one to be substituted for another. The
selection of relevant descriptors is a well-known problem and given a
large collection of them, approaches to identify a suitable subset
have been discussed extensively in the
literature~\cite{Miller:2002aa,Kohavi:1997gf}.
